### 2016-09-29 rebuttal.tex

\question The code in line 210 should be made into its own line (like a displaymath formula), for typesetting reasons and better readability.
\begin{solution}
We now use a verbatim environment here.
\end{solution}

\question The footnote 4 should be moved from line 221 to line 222, right after ``Basic''.
\label{rev3point16}
\begin{solution}
We have made the suggested change.
\end{solution}

\question The part ``which defines some basic methods for symbolic expression trees'' should be removed from line 222, as it was already given in line 130.
\begin{solution}
This part was removed and footnote moved to the mentioned
text in the section~\ref{P-sec:core}, ``The Core''.
\end{solution}

\question In line 225, the sentence ``Not all SymPy classes are subclasses of \texttt{Expr}.'' sounds confusing as a reader new to SymPy wouldn't expect, for example, symbols to inherit ``Expr''. It would be better to expand this, for example ``Most of the SymPy classes (including \texttt{Symbol}) are subclasses of \texttt{Expr}, but there are exceptions to this rule''.
\begin{solution}
This paragraph now reads:
\begin{quote}
  The typical way to create a custom SymPy object is to subclass an existing
  SymPy class, usually \texttt{Basic}, \texttt{Expr}, or \texttt{Function}. As
  it was stated before, all SymPy classes used for expression trees should be
  subclasses of the base class \texttt{Basic}. \texttt{Expr} is the
  \texttt{Basic} subclass for mathematical objects that can be added and
  multiplied together. The most commonly seen classes in SymPy are subclasses
  of \texttt{Expr}, including \texttt{Add}, \texttt{Mul}, and \texttt{Symbol}.
  Instances of \texttt{Expr} typically represent complex numbers, but may also
  include other ``rings'', like matrix expressions. Not all SymPy classes are
  subclasses of \texttt{Expr}. For instance, logic expressions, such as
  \verb|And(x, y)|, are subclasses of \texttt{Basic} but not of \texttt{Expr}.
\end{quote}
\end{solution}

### 2016-09-29 rebuttal.tex

\item The SymPy Live section was short and would be mostly duplicated by the
  paragraph that has been added to the introduction in the paper. We have thus
  removed it.
\end{itemize}

We also consider the supplement sections (previously) 2, 3, 4, and
6---``Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript:

\begin{itemize}
\item The ``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.

\item The ``Logic'' section is alluded to in the ``Assumptions'' subsection,
  and the module is briefly mentioned in the ``Extensibility'' section,
  but is not discussed in depth in the main manuscript. While the logic
  submodule is indeed important for certain parts of SymPy, we do not consider
  it to be of interest to the general reader. Furthermore, on a technical
  note, the assumptions discussed in the manuscript are the so-called ``old
  assumptions'', which do not use the \texttt{sympy.logic} submodule discussed
  in the supplement (they use an implementation of the Rete algorithm, which
  is separate from \texttt{sympy.logic}). The so-called ``new assumptions'',
  mentioned briefly in the ``Conclusion and Future Work'' section, does use
  it, but we have opted to not discuss this module in depth, as it is still in
  development and not fully usable. We have added some text to the assumptions
  section discussing this and referencing the logic subsection of the
  supplement (see footnote~\ref{P-note:assumptions}).

### 2016-09-29 rebuttal.tex

\question The footnote 4 should be moved from line 221 to line 222, right after ``Basic''.
\label{rev3point16}
\begin{solution}
We have made the suggested change.
\end{solution}

\question The part ``which defines some basic methods for symbolic expression trees'' should be removed from line 222, as it was already given in line 130.
\begin{solution}
This part was removed and footnote moved to the mentioned
text in the section~\ref{P-sec:core}, ``The Core''.
\end{solution}

\question In line 225, the sentence ``Not all SymPy classes are subclasses of \texttt{Expr}.'' sounds confusing as a reader new to SymPy wouldn't expect, for example, symbols to inherit ``Expr''. It would be better to expand this, for example ``Most of the SymPy classes (including \texttt{Symbol}) are subclasses of \texttt{Expr}, but there are exceptions to this rule''.
\begin{solution}
This paragraph now reads:
\begin{quote}
  The typical way to create a custom SymPy object is to subclass an existing
  SymPy class, usually \texttt{Basic}, \texttt{Expr}, or \texttt{Function}. As
  it was stated before, all SymPy classes used for expression trees should be
  subclasses of the base class \texttt{Basic}. \texttt{Expr} is the
  \texttt{Basic} subclass for mathematical objects that can be added and
  multiplied together. The most commonly seen classes in SymPy are subclasses
  of \texttt{Expr}, including \texttt{Add}, \texttt{Mul}, and \texttt{Symbol}.
  Instances of \texttt{Expr} typically represent complex numbers, but may also
  include other ``rings'', like matrix expressions. Not all SymPy classes are
  subclasses of \texttt{Expr}. For instance, logic expressions, such as
  \verb|And(x, y)|, are subclasses of \texttt{Basic} but not of \texttt{Expr}.
\end{quote}
\end{solution}

\question The title ``Features'' in line 276 is ambiguous, as a ``feature''
has no precise meaning in Python (or even software libraries in general). It
should be replaced by ``Packages and modules'' or a similar more precise
wording. The same goes for ``feature'' in most other places in the paper (for
example, the caption of Table 1.\ and line 495). It would be very useful to also include actual names of the packages/modules in Table 1., as well as in any section covering those packages/modules.
\begin{solution}
IEEE 829 defines the term feature as ``a distinguishing
characteristic of a software item (e.g., performance, portability,
or functionality).''  We believe that this definition fits our needs. Note
that we have renamed section (now)~\ref{P-sec:features} to ``Overview of Capabilities''.

Table~\ref{P-features-table} was extended to include submodule names.
\end{solution}

### 2016-09-29 printers.tex
Replace repr quote in rebuttal with cross reference

SymPy has a rich collection of expression printers. By default, an interactive
Python session will render the \verb|str| form of an expression, which has
been used in all the examples in this paper so far. The \verb|str| form of an
expression is valid Python and roughly matches what a user would type to enter
the expression.\footnote{Many Python libraries distinguish the \texttt{str}
  form of an object, which is meant to be human-readable, and the
  \texttt{repr} form, which is mean to be valid Python that recreates the
  object. In SymPy, \texttt{str(expr) == repr(expr)}. In other words, the
  string representation of an expression is designed to be compact,
  human-readable, and valid Python code that could be used to recreate the
  expression. As it was noted in section~\ref{sec:core}, the \texttt{srepr}
  function prints the exact, verbose form of an expression.}

>>>>

SymPy has a rich collection of expression printers. By default, an interactive
Python session will render the \verb|str| form of an expression, which has
been used in all the examples in this paper so far. The \verb|str| form of an
expression is valid Python and roughly matches what a user would type to enter
the expression.\footnote{\label{note:repr}Many Python libraries distinguish the \texttt{str}
  form of an object, which is meant to be human-readable, and the
  \texttt{repr} form, which is mean to be valid Python that recreates the
  object. In SymPy, \texttt{str(expr) == repr(expr)}. In other words, the
  string representation of an expression is designed to be compact,
  human-readable, and valid Python code that could be used to recreate the
  expression. As it was noted in section~\ref{sec:core}, the \texttt{srepr}
  function prints the exact, verbose form of an expression.}
